\documentclass{ximera}
\input{../preamble.tex}
\author{Anastasiia Holovchenko \and Anna Davis (project advisor)} \title{Informed Consent} 
\begin{document}
\begin{abstract}
\end{abstract}
\maketitle 

\textbf{Title:} \emph{Development and evaluation of an interactive, electronic statistics module, covering the Central Limit Theorem, in response to the rising cost of textbooks.}

\textbf{Investigator:} Anastasiia Holovchenko, Ohio Dominincan University

\textbf{Advisor:} Anna Davis, Ohio Dominican University

\textbf{Source of Support:} This study is being performed as partial fulfillment of the requirements for the Honors Program at Ohio Dominican University.

\textbf{Purpose:} You are being asked to participate in a research project that seeks to develop and investigate the effectiveness of Central Limit Theorem module by completing an assignment.

\textbf{Risks and Benefits:} There are no risks greater than those encountered in everyday life.

\textbf{Compensation:} There will be no financial compensation. You will receive a grade for the assignment provided in the module. If you do not wish to have your data used in the study, you will be given a chance to opt out of the study, but you will still be required to complete the assignment for a grade.

\textbf{Confidentiality:} Event-stream data from user interactions with the platform -- such as mouse clicks, and submitted answers -- are stored on a secure server at the Ohio State University.  The system does NOT require a log-in, and does NOT collect identifiable personal information.  If you give consent to have your event-stream data used in this research project, researchers will work with an anonymized event log that cannot be traced back to you. If you do not give your consent, your event log will not be used in analysis.  

\textbf{Right to Withdraw:} You are under no obligation to participate in this study.  You are free to withdraw your consent to participate at any time while completing the task. 

\textbf{Summary of Benefits:} A summary of the results of this research will be supplied to you at no cost, upon request.  

\textbf{Voluntary Consent:} I have read the Consent Form and understand what is being requested of me.  I also understand that my participation is voluntary and that I am free to withdraw consent at any time, for any reason while accessing this platform.  

\textbf{Contact Info:}  I understand that should I have further questions about my participation in this study, I may email holovcha@ohiodominican.edu

\textbf{Researcher’s Name:} Anastasiia Holovchenko


\end{document}